MSF_Groupwork-NBA_shotlog

### 2016-10-10 MSFGroupwork-NBAHotHand.Rmd
calculate distance

#select data with only scored result
#Point type (2 or 3 points) and distance
point_type <- c()
distance <- c()
for (z in 1:nrow(df)){
  if(df[z, "SHOT_RESULT"] == 1 & df[z, "PTS_TYPE"] >= 1){
    point_type <- c(point_type, df[z, "PTS_TYPE"])
    distance <- c(distance, df[z, "CLOSE_DEF_DIST"])
  }
}

#combine point type and distance
valid_distance = data.frame(point_type, distance)

@@

@@

@@

#combine 2 point players and defender distance
player2point <- data.frame(players2, distance2)
summary(player2point)

>>>>

#select data with only scored result
#Point type (2 or 3 points) and distance
point_type <- c()
distance <- c()
shot_dist <- c()
for (z in 1:nrow(df)){
  if(df[z, "SHOT_RESULT"] == 1 & df[z, "PTS_TYPE"] >= 1){
    point_type <- c(point_type, df[z, "PTS_TYPE"])
    distance <- c(distance, df[z, "CLOSE_DEF_DIST"])
    shot_dist <- c(shot_dist, df[z, "SHOT_DIST"])
  }
}

#combine point type and distance
valid_distance = data.frame(point_type, distance, shot_dist)
dist_group <- c(5, 10, 15, 20, 25, Inf)
valid_distance[, "Range Group"] <- c(findInterval(valid_distance$distance, dist_group))

@@

#calculate correlation between defender distance and shot distance (2 or 3 points)
cor(distance, shot_dist)

@@

ggplot(data = valid_distance, aes(x = distance, y = shot_dist)) + geom_point()

ggplot(data = valid_distance, aes(x = distance) + geom_bar())

@@

#combine 2 point players and defender distance
player2point <- data.frame(players2, distance2)

summary(player2point)

#calculate mean distance from 2-pointers
avg_dist2 <- aggregate(distance2 ~ players2, player2point, mean)
